---
title: "Lab 03 - Great Lakes Fish Stocking"
author: "Nyla Williams"
date: "Feb 14, 2024"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, warning = FALSE}
fish_stock <- read_csv("../data/great-lakes-fish-stock.csv")
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.
```{r - glimpse fish}
glimpse(fish_stock)
```

##How many observations and how many variables are in the dataset? Use inline code to answer this question
```{r}
nrow(fish_stock)
ncol(fish_stock)
```

##What does each row represent? Be specific!
Each row represents a characteristic property of a certain fish


### Exercise 2

```{r - salmon stock}
salmon_stock <- fish_stock %>%
  filter(
    SPECIES %in% c("ATS", "CHS", "COS"),
    !is.na(WEIGHT),
     LAKE != "ON"
  )

```

```{r}
nrow(salmon_stock)
ncol(salmon_stock)
names(salmon_stock)
```

### Exercise 3


```{r}
salmon_stock <- fish_stock %>% mutate( AVERAGE_WEIGHT = WEIGHT / NO_STOCKED * 1000 )
```

This code chunk will modify already existing variables; The function creates a new data frame that basically contains the variables from fish stock and the "AVERAGE" weight.
### Exercise 4


```{r}
fish_stock %>% 
  filter(YEAR > 2000) %>% 
  group_by(YEAR) %>% 
  summarize(MEAN_NO_STOCKED = mean(NO_STOCKED, na.rm = TRUE), 
            MEAN_WEIGHT = mean(WEIGHT, na.rm = TRUE)) %>% 
  arrange(desc(MEAN_NO_STOCKED))
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.